Manuscript

### 2015-03-14 inst/simulation/manuscript.Rmd
...

library(raster)
mss <- getMSS("E")
study <- mss$study
surveyRoutes <- mss$getSurveyRoutes()
#habitatTypes <- raster::extract(habitat, surveyRoutes$surveyRoutes[1:3])

@@

```{r figure-4-init}
getPopulationCorrelations <- function(scenarios, modelNames, cutoff=c(-Inf,Inf)) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  return(populationCorrelations)
}

plotPopulationCorrelations <- function(populationCorrelations, case) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  ggtitle(paste("Case:", case)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.title=element_text(size=10),
                                      plot.margin=unit(c(0.2, 0, 0, 0), units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

```{r figure-4abc}
pc1 <- getPopulationCorrelations(scenarios=scenarios, modelNames=modelNames[1], cutoff=cutoff)
pc2a <- getPopulationCorrelations(scenarios="Acombined", modelNames=modelNames[1], cutoff=cutoff)
pc2b <- getPopulationCorrelations(scenarios="Bcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2c <- getPopulationCorrelations(scenarios="Ccombined", modelNames=modelNames[1], cutoff=cutoff)
pc2d <- getPopulationCorrelations(scenarios="Dcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2e <- getPopulationCorrelations(scenarios="Ecombined", modelNames=modelNames[1], cutoff=cutoff)
pc2f <- getPopulationCorrelations(scenarios="Fcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2 <- rbind(pc2a,pc2b,pc2c,pc2d,pc2e,pc2f)
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)

>>>>

library(raster)
mss <- getMSS("E")
study <- mss$study
surveyRoutes <- study$surveyRoutes
#habitatTypes <- raster::extract(habitat, surveyRoutes$surveyRoutes[1:3])

@@

```{r figure-4}
getPopulationCorrelations <- function(scenarios, modelNames, cutoff=c(-Inf,Inf)) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  return(populationCorrelations)
}

plotPopulationCorrelations <- function(populationCorrelations, case) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  ggtitle(paste("Case:", case)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.title=element_text(size=10),
                                      plot.margin=unit(c(0.2, 0, 0, 0), units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}

pc1 <- getPopulationCorrelations(scenarios=scenarios, modelNames=modelNames[1], cutoff=cutoff)
pc2a <- getPopulationCorrelations(scenarios="Acombined", modelNames=modelNames[1], cutoff=cutoff)
pc2b <- getPopulationCorrelations(scenarios="Bcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2c <- getPopulationCorrelations(scenarios="Ccombined", modelNames=modelNames[1], cutoff=cutoff)
pc2d <- getPopulationCorrelations(scenarios="Dcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2e <- getPopulationCorrelations(scenarios="Ecombined", modelNames=modelNames[1], cutoff=cutoff)
pc2f <- getPopulationCorrelations(scenarios="Fcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2 <- rbind(pc2a,pc2b,pc2c,pc2d,pc2e,pc2f)
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)
